Communicating with convexity

### 2017-11-10 article_cvxpy.tex
updated text to be more consistent with code and vice versa

% Front article
% -----
	\NewsItem{\noindent``Nothing takes place in the world whose meaning is not that of some maximum or minimum.''}
	\NewsAuthor{Leonard Euler (1707-1783)}

@@

Supposing that we want to receive a signal at receiver $i$ from transmitter $k$, we define the recipient matrix, $\delta$, as
\begin{align*}
\delta_{ij} = \begin{cases}
1, \quad j=k\\
0, \quad j\neq k
\end{cases},
\end{align*}
and our signal potential matrix $\hat{S}$ as $\hat{S} = G*\delta$.  This means that signal received at transmitter $i$ is, $S_i = \hat{S}_{ik}p_k = G_{ik}p_k$.
% The desired signal for receiver $i$ is $S_i = G_{ik}p_k$, 
While the interference potential matrix is defined as $\hat{I} = G-\hat{S}$, giving the interference at $i$ is $I_i = (\hat{I}*p)_i = \sum_{j\neq k}G_{ij}p_j$. We must note that DCP does not allow division of the optimisation variable $p_i$, as it cannot guarantee curvature, so  
\begin{equation*}
  \gamma_i \geq \gamma_0\Longleftrightarrow  \frac{S_i}{\sigma_i + I_i} = \frac{G_{ik}p_k}{\sigma_i+\sum_{j\neq k}G_{ij}p_j} \geq \gamma_0, \quad \forall i
\end{equation*}
is rearranged to,
\begin{equation*}
S_i-\gamma_0(\sigma_i + I_i)\geq 0, \quad \forall i
\end{equation*} which is affine, and hence a DCP function.

\subsection{Path gain}
%\noindent The path gain $G_{ij}$ represents the proportion of power that reaches receiver $i$ from transmitter $j$. Supposing that the desired signal to receiver $i$ is from transmitter $k$, the power received is,
%\begin{equation}
%p_{ik}^{\text{rec}} = G_{ik}p_k.
%\end{equation}
%Denoting the SINR at $i$ by $\gamma_i$, we have
%\begin{equation}
%\gamma_i = \frac{G_{ik}p_k}{\sigma_i+\sum_{j\neq k}G_{ij}p_j}
%=\frac{S_i}{\sigma_i+I_i}.
%\end{equation}
\noindent In a physical context, the path gain from transmitter $j$ to receiver $i$, as shown in Fig.~\ref{fig:pathgain}, will depend on the distance, $d_{ij}$ between them. Assuming isotropic propagation from each transmitter, the fraction of power from $j$ that reaches $i$ is:
\begin{equation}
G_{ij} = k_i/d_{ij}^\alpha
\end{equation}
where $\alpha$ is the pathloss coefficient and $k$ is a proportionality constant specific to the receiver $i$.  For free space $\alpha = 2$, while in urban environments $\alpha \sim 3.5$ \cite{hata1980}. Further physical complexities, such as the stochastic effects from Rayleigh fading can be easily incorporated, whilst remaining within the DCP framework.

@@

For paired transmitters and receivers ($k=i$), we randomly sample distances $d$ from a scaled $\beta(2,2)$ distribution, such that $d_{ii} \sim 0.2\times\text{Beta}(2,2)$.  For unpaired transmitters and receivers ($k\neq i$), we randomly sample distances $d$ from a uniform distribution, such that $d_{ik} \sim \text{Uniform}(0,1)$.\\

We have chosen the background noise vector $\sigma$ as constant for each receiver, with $\sigma_i = 5$.

\subsection{Example code}
\noindent To indicate the brevity of code implementation in \texttt{cvxpy} we show a minimal working example below: \lstinputlisting[language=Python,mathescape=true,inputencoding=utf8,literate={δ}{$\delta$}1 {σ}{$\sigma$}1 {γ}{$\gamma$}1 {∈}{$\in$}1 ]{minimisePgivenSINR.py}

>>>>

% Front article
% -----
	\NewsItem{\noindent``Nothing takes place in the world whose meaning is not that of some maximum or minimum.''}
	\NewsAuthor{Leonhard Euler (1707-1783)}

@@

Supposing that we want to receive a signal at receiver $i$ from transmitter $k$, we define the recipient matrix, $\delta$, as
\begin{align*}
\delta_{ij} = \begin{cases}
1, \quad j=k\\
0, \quad j\neq k
\end{cases},
\end{align*}
and our signal potential matrix $\hat{S}$ as $\hat{S} = G*\delta$.  This means that signal received at transmitter $i$ is, $S_i = \hat{S}_{ik}p_k = G_{ik}p_k$.
% The desired signal for receiver $i$ is $S_i = G_{ik}p_k$, 
While the interference potential matrix is defined as $\hat{I} = G-\hat{S}$, giving the interference at $i$ is $I_i = (\hat{I}*p)_i = \sum_{j\neq k}G_{ij}p_j$. We must note that DCP does not allow division of the optimisation variable $p_i$, as it cannot guarantee curvature, so  
\begin{equation*}
  \gamma_i \geq \gamma_0\Longleftrightarrow  \frac{S_i}{\sigma_i + I_i} = \frac{\hat{S}_{ik}p_k}{\sigma_i+(\hat{I}*p)_i} \geq \gamma_0, \quad \forall i
\end{equation*}
is rearranged to,
\begin{equation*}
\hat{S}_{ik}p_k-\gamma_0(\sigma_i + (\hat{I}*p)_i)\geq 0, \quad \forall i,
\end{equation*} 
which is affine, and hence a DCP function.

\subsection{Path gain}
%\noindent The path gain $G_{ij}$ represents the proportion of power that reaches receiver $i$ from transmitter $j$. Supposing that the desired signal to receiver $i$ is from transmitter $k$, the power received is,
%\begin{equation}
%p_{ik}^{\text{rec}} = G_{ik}p_k.
%\end{equation}
%Denoting the SINR at $i$ by $\gamma_i$, we have
%\begin{equation}
%\gamma_i = \frac{G_{ik}p_k}{\sigma_i+\sum_{j\neq k}G_{ij}p_j}
%=\frac{S_i}{\sigma_i+I_i}.
%\end{equation}
\noindent In a physical context, the path gain from transmitter $j$ to receiver $i$, as shown in Fig.~\ref{fig:pathgain}, will depend on the distance, $d_{ij}$ between them. Assuming isotropic propagation from each transmitter, the fraction of power from $j$ that reaches $i$ is:
\begin{equation}
G_{ij} = A_i/d_{ij}^\alpha
\end{equation}
where $\alpha$ is the pathloss coefficient and $k$ is a proportionality constant specific to the receiver $i$.  For free space $\alpha = 2$, while in urban environments $\alpha \sim 3.5$ \cite{hata1980}. Further physical complexities, such as the stochastic effects from Rayleigh fading can be easily incorporated, whilst remaining within the DCP framework.

@@

All the parameters we will take as dimensionless to give simple numbers to work with.  The maximum available power, $P_{\text{max}}$ is set to 1.  We have chosen the background noise vector $\sigma$ as constant for each receiver, with $\sigma_i = 5$.  Similarly, the receiver coefficient $A$ was set to $0.025$ for each receiver. \\

To generate the gain matrix $G$, we randomly sample distances from a given distribution.  For paired transmitters and receivers ($k=i$), we sample $d$ from a scaled $\beta(2,2)$ distribution, such that $d_{ii} \sim 0.2\times\text{Beta}(2,2)$.  For unpaired transmitters and receivers ($k\neq i$), we sample $d$ from a uniform distribution, such that $d_{ik} \sim \text{Uniform}(0,1)$.\\

\subsection{Example code}
\noindent To indicate the brevity of code implementation in \texttt{cvxpy} we show a minimal working example below.  For the random seed of 100 given, the optimal total power consumption is $P = 0.381$, with $p_1,p_2,p_3 = (0.139, 0.072, 0.169)$.  Around 70\% of the simulations with these parameters have a feasible solution, with an average optimal power consumption of $P\sim0.4$.

\lstinputlisting[language=Python,mathescape=true,inputencoding=utf8,literate={δ}{$\delta$}1 {σ}{$\sigma$}1 {γ}{$\gamma$}1 {∈}{$\in$}1 ]{minimisePgivenSINR.py}
